---
title: "Condensed Scraper of YouTube Comments for Modeling with Wordfish"
author: "Jeff Antsen, Nicole Lemire Garlic, Alex Wermer-Colan"
date: "6/16/2020"
output:
  html_document: default
  pdf_document: default
---

# 0: SETUP
### Set code block default prefs
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(eval=TRUE)
```

### Install Packages
```{r install_packages, eval=FALSE}
#Install Packages and Library Calls
#install.packages("knitr")
#install.packages("NLP")
#install.packages("tm")
#install.packages("tidyverse")
#install.packages("ggplot2")
#install.packages("austin", repos="http://R-Forge.R-project.org")
#install.packages("beepr")
#install.packages("RColorBrewer")
#install.packages("tuber")
#install.packages("gtools")
#install.packages("data.table")
#install.packages("lubridate")
```

### Call Libraries
```{r call_libraries, echo=FALSE, results='hide'}
# CLEANUP your workspace (before running / rerunning code)
rm(list=ls())

# Call Libraries
#library(kintr)
library(NLP)
library(tm)
library(tidyverse)
library(ggplot2)
library(austin)
library(beepr)
library(RColorBrewer)
library(tuber)
library(gtools)
library(data.table)
library(lubridate)
```

### Authorize your API account
Remember to push 1 for 'yes; in the CONSOLE! And then log into your gmail/google account.
```{r authorize, echo=TRUE, results='hide'}
#the first time you authorize your credentials, at prompt choose "1: Yes IN THE CONSOLE!"
source("Config.R")
app_id <- API_ID
app_secret <- API_Secret
yt_oauth(app_id, app_secret) 
```


### Read In Parameters / Tolerances from the Config file
~~ Can add additional parameters to the Config file
```{r Parameters_and_Tolerances_From_Config, echo=FALSE, results='hide'}
# Read in Subject / Terms from Config.R
subject_s <- Subject
SearchTerms <- Search

# Read in search dates from Config.R
BeforeSearchDate <- BeforeDate
AfterSearchDate <- AfterDate

# Read in data refinement options from Config.R
OnlyTopVideos      <- top_N_videos[1]  # T/F - do this or not?
NumbVideos         <- top_N_videos[2]  # if so, what value?

KeepMinComments    <- atleast_M_comments[1] # T/F - do this or not?
MinComments        <- atleast_M_comments[2] # if so, what value?
```


# 1: SCRAPING DATA - 'code' begins here
### Get list of videos matching your search terms and organize that video list
```{r get_video_list}
SearchResults <- map(SearchTerms, yt_search)
SearchResultsDF <- do.call(rbind, lapply(SearchResults, data.frame))
SearchResultsDF[] <- lapply(SearchResultsDF, as.character)
SearchResultsDF$publishedAt <- SearchResultsDF$publishedAt %>% as_datetime(tz = "UTC", format = NULL)
SearchResultsDF <- select(SearchResultsDF, video_id, publishedAt, title, channelTitle) %>% arrange(desc(publishedAt))
SearchResultsDF <- SearchResultsDF %>% filter(publishedAt > AfterSearchDate & publishedAt < BeforeSearchDate)
video_list <-as.vector(SearchResultsDF$video_id) #final list of video IDs
length(video_list)
```
IF YOU ARE USING YOUR OWN VIDEO LIST, skip to the end of this chunk and create your own vector of video ID strings

### Scrape available comments on each of those videos
This chunk gets all available video comments from API, and converts to a dataframe. It uses `r possibly()` to avoid error messages for unavailable videos comments.
```{r scrape_available_comments, warning=FALSE}
# video_list <-c("MAKE", "YOUR", "OWN")
get_avlbl_comments <- possibly(get_all_comments, otherwise = NULL)
AllComments <- map(video_list, get_avlbl_comments)
AllCommentsDF <- do.call(smartbind, lapply(AllComments, data.frame))  # this works but returns a BUNCH of warnings
nrow(AllCommentsDF)
AllCommentsVideos <- unique(AllCommentsDF$videoId)  #stores which video comments were scraped
#View(AllComments[[3]])
```


```{r how_many_videos}
print(paste("You have identified", nrow(AllCommentsDF), "comments from", length(AllCommentsVideos), "unique videos identified using the", length(SearchTerms) ,"tags: ", paste(SearchTerms, collapse=", "),"."))
```


### Merge Metadata (includes video titles) from Search Results
```{r join_metadata}
#joins video metadata to comments and renames columns for clarity
AllCommentsMetadata <- inner_join(AllCommentsDF, SearchResultsDF, by = c("videoId" = "video_id"))
AllCommentsMetadata <- rename(AllCommentsMetadata, c(commentPublishedAt = publishedAt.x,
                                                     commentUpdatedAt = updatedAt,
                                                     commentLikeCount = likeCount,
                                                     commentId = id,
                                                     videoPublishedAt= publishedAt.y,
                                                     videoTitle = title,
                                                     videoChannelTitle = channelTitle))
#View(AllCommentsMetadata)
```

# 2: SAVE and READ DATA
### Recommended -- Save Your Data
```{r output_comments, eval=FALSE, echo=FALSE}
write.csv(AllCommentsMetadata, paste("Data/AllComments__", subject_s, today("EST"),".csv", sep=""))
```

### And, read data back in here (only if you need to!)
```{r read_in_data, warnings=FALSE}
#yourdata <- read.csv(paste("Data/AllComments_", subject_s, "_", today("EST"), ".csv", sep="")) 
#View(yourdata)  #@ if not using data scraped with this tool, you may need to do reformatting (changing col names, etc)
#nrow(yourdata)
#AllCommentsMetadata <- yourdata
```

# 3: DATA CLEANING
```{r select_comments_basedOn_parameters}
totalScraped <- AllCommentsMetadata %>% group_by(videoTitle) %>% tally() %>% arrange(desc(n))
nrow(AllCommentsMetadata)

#Two options:
#1. remove videos with less than M comments and view final count
if(KeepMinComments == TRUE){
tooFew <- filter(totalScraped, n < MinComments)
AllCommentsMetadata <- AllCommentsMetadata %>% anti_join(tooFew)
AllCommentsMetadata %>% group_by(videoTitle) %>% tally() %>% arrange(desc(n))  # how many comments, from which video, remain?
}
nrow(AllCommentsMetadata)

#AND/OR
#2. keep N videos with highest number of comments
if(OnlyTopVideos == TRUE){
Discards <- totalScraped[-(1:NumbVideos), ]
AllCommentsMetadata <- AllCommentsMetadata %>% anti_join(Discards)
AllCommentsMetadata %>% group_by(videoTitle) %>% tally() %>% arrange(desc(n)) # # how many comments, from which video, remain?
}
nrow(AllCommentsMetadata)
```


###tokenize those longer comments
```{r tokenize_elaborate_comments, echo=FALSE, results='hide'}
comment_tokens_l <- list()

for (com in 1:nrow(AllCommentsMetadata)) {
  sto <- AllCommentsMetadata$textOriginal[com]
        #@ preprocess each comment, keep
  stolist <- list()
  sto <- tolower(sto)
  sto_list <- strsplit(sto, "\\W")
  sto_text <- unlist(sto_list)
  sto_rm <- sto_text[-which(sto_text == "")]; sto_text <- sto_rm
  if(length (sto_text) >= 8 & length(unique(sto_text)) >=5) {   #@ comments with at least 8 words, 5 of which are unique
        #@ create list.head               
    list.head <- paste(AllCommentsMetadata$videoTitle[com], "%_%", com,"%_%", AllCommentsMetadata$commentId[com], "%_%", AllCommentsMetadata$videoChannelTitle[com], sep="")
    comment_tokens_l[[list.head]] <- sto_text
  }}

comment_ids <- names(comment_tokens_l)
length(comment_tokens_l)
```

```{r how_many_comments_1}
print(paste("keeping",length(comment_tokens_l), "out of", nrow(AllCommentsMetadata),"comments ;",round((length(comment_tokens_l)/nrow(AllCommentsMetadata))*100, 2), "% of total comments kept" ))
```

### Making the Corpus
```{r data_reshape_for_WF, echo=FALSE, warning=FALSE, results='hide'}
#Turn the list of comment files into a corpus data object
comment_corpus <- Corpus(VectorSource(comment_tokens_l))   #@ this function needs a list of tokenized char vectors
comment_corpus <- tm_map(comment_corpus, removeNumbers)
comment_corpus <- tm_map(comment_corpus, removePunctuation)

for(com in 1:length(comment_corpus)){  # remove the leading "c"s added when the corpus command concatonates tokens 
  if(substr(comment_corpus[[com]]$content,1,1)=="c"){
    comment_corpus[[com]]$content<- substr(comment_corpus[[com]]$content, 2, nchar(comment_corpus[[com]]$content))}}

my_stop <- c(stopwords("english"),
             "c","x", "s", "t", "m", "amp", "youtube", "www", "com", "quot", "br", "http", "https", "")

comment_corpus <- tm_map(comment_corpus, removeWords, my_stop)

#The DocumentTermMatrix
dtm = DocumentTermMatrix(comment_corpus)
dtm   # old DTM has 56,732 terms, new has 52,297 - removed 4435 terms caused due to leading "c"s
```

### Control Sparseness, pre remvoing bad comments
```{r DTM_sparsity_control, echo=TRUE, results='hide'}
# Set accepted sparsity parameter
sparsity <- .9977
dtma = removeSparseTerms(dtm, sparse = sparsity)
dtma
```

### Identify Problem Comments, and remove them
```{r which_com_have_0_words_left?}
problem_comments <- NA

while(length(problem_comments) > 0 ) { 

dtma_matrix <- as.matrix(dtma)

problem_comments <- NA
for(com in 1:nrow(dtma_matrix) ){                 # Identify problem comments
  if(sum(dtma_matrix[com,]) < 11 ){
    #print(comment_corpus[[com]]["content"])
    problem_comments <- c(problem_comments, com)
  }}
#print(problem_comments)
problem_comments <- problem_comments[(-1)];       # Delete the leading NA - then, if no problem comments, this will be length 0

if(length(problem_comments) > 0 ){                # Remove the problem comments and their corresponding titles
  print(paste("removing", length(problem_comments), "problem comments"))
  comment_corpus <- comment_corpus[(-problem_comments)]  
  comment_ids <- comment_ids[(-problem_comments)]
} else {
    print("There don't appear to be any [more] comments with too few words")
  }

dtm1 <-DocumentTermMatrix(comment_corpus)  # make new DTM

dtma <- removeSparseTerms(dtm1, sparse=sparsity) # and remove sparse terms again
rm(dtma_matrix)  #@ remove the ponderous dtma_matrix object
}
length(comment_ids)
```

```{r how_many_comments_2}
print(paste("Modeling",length(dtma$dimnames$Terms),"words from", length(dtma$dimnames$Docs), "comments with a usable number of tokens, of the original", nrow(AllCommentsMetadata), "comments.",round((length(dtma$dimnames$Docs))/nrow(AllCommentsMetadata)*100, 2) , "% of total comments kept from initial scrape... now trying to WF!"))
```

# 4: FISHIN for Words!
```{r WORDFISH}
#Running a wordfish model
possibly_fish <- possibly(wordfish, otherwise=NULL)
wfa1 <- possibly_fish(as.wfm(dtma), dir=c(1, 2), control = list(tol = 3.0e-5), verbose = T)

wfa1$docs <- comment_ids
str(wfa1)
```


### Store data from WF model as independant objects (helpful for later manipulation)
```{r store_WF_model_data, echo=FALSE}
wfdocs_v <- wfa1$docs
theta <- wfa1$theta
alpha <- wfa1$alpha

wfwords_v <- wfa1$words
beta <- wfa1$beta
psi <- wfa1$psi
```

### View some properties of the WF model (not necessary)
```{r view_WF_model_properties, echo=TRUE}
sum(theta[which(theta>0)])
sum(theta[which(theta<0)])
mean(theta)
sum(theta)

### View a histogram of the distribution of each key variable
hist(theta, breaks=30)  # document polarity (refined iteratively)
hist(alpha, breaks=30)  # fixed effect for document length
hist(beta, breaks=50)   # word polarity (refined iteratively)
hist(psi, breaks=50)    # fixed effect for term (aka ~type~) frequency

```

### Make Composite Data Objects
```{r make_WF_data_objects, echo=FALSE, results='hide'}
comment_identifiers<-data.frame(NA, NA, NA, NA, NA, NA)
colnames(comment_identifiers) <- c("short_title","short_channel","video_title", "comment_number", "comment_id", "video_channel")

for (com in 1:length(wfdocs_v)){
split <- unlist(strsplit(wfdocs_v[com], "%_%"))
comment_identifiers[com,3:6] <- split
title <- unlist(strsplit(comment_identifiers$video_title[com], " "))
channel <- unlist(strsplit(comment_identifiers$video_channel[com], " "))
#                      s_title <- paste(title[1:4], collapse=" ")
s_title <- title[1]               # make the 'short title' - first 5 words with 3+ chars
for(t_word in 2:length(title)){
  if(nchar(title[t_word]) > 2) {
    s_title <- c(s_title, title[t_word])
  }}
  if(length(s_title > 4)) {
  s_title <- s_title[1:5]}
s_title <- paste(s_title, collapse=" ")
comment_identifiers$short_title[com] <- s_title  
}

### CREATE DOC DATA DATAFRAME
wf_docdata.df <- data.frame(theta, alpha, comment_identifiers, wfdocs_v)
#View(wf_docdata.df)

### CREATE WORD DATA DATAFRAME
wf_worddata.df <- data.frame(wfwords_v, beta, psi)
```

# 5: VISUALIZATIONS
### Comment (doc) polarity, color by video 'short title'
```{r comments_by_shorttitle, echo=FALSE}
short_title_T_A_plot <- ggplot(data = wf_docdata.df,
                                   mapping = aes(x =theta, y = alpha, label = comment_number, color=short_title))+
  geom_text(size = .8) +
  labs(x = "Comment polarity: an optimized value (theta)", y = "Comment length: a fixed effect (alpha)") +
  guides(size = "none", color = guide_legend("")) + theme(legend.position="bottom") +
  theme(legend.text = element_text(size=4)) +
  labs(title = paste("Polarity of ", subject_s, "comments on YouTube, colorized by Video"),
                      subtitle= paste("identified using the tags:", paste(SearchTerms, collapse=" ")))
short_title_T_A_plot

ggsave(paste("Visualizations/",subject_s, "__shorttitle_T_A_plot_", today("EST"),".pdf",sep=""), device="pdf")
```

### Comment (doc) polarity, color by video
```{r another_comment_plot2, eval=F, echo=F}
channel_T_A_plot <- ggplot(data = wf_docdata.df, mapping = aes(x =theta, y = alpha, label = comment_number, color=video_channel))+ geom_text(size = .8) +
  labs(x = "Comment polarity: an optimized value (theta)", y = "Comment length: a fixed effect (alpha)") +
  guides(size = "none", color = guide_legend("")) + theme(legend.position="bottom") +
  theme(legend.text = element_text(size=4)) +
  labs(title = paste("Polarity of ", subject_s, "comments on YouTube, colorized by Video Channel"),
                      subtitle= paste("identified using the tags:", paste(SearchTerms, collapse=" ")))
channel_T_A_plot

ggsave(paste("Visualizations/",subject_s, "__channel_T_A_plot_", today("EST"),".pdf",sep=""), device="pdf")
```


### Comment words (tokens) polarity scatter
```{r word_scatterfish}
word_P_B_plot <- ggplot(data = wf_worddata.df, mapping = aes(x = beta, y = psi, label = wfwords_v)) +
  geom_text(data=subset(wf_worddata.df, psi>-8), size = 0.755) +
  labs(x = "Word polarity: an optimized value (beta)", y = "Word frequency: a fixed effect (psi)") +
  #guides(size = "none", color = guide_legend("")) +
  labs(title = paste("Polarity of typical words used in", subject_s, "YouTube comments"),
                   subtitle= paste("identified using the tags:", paste(SearchTerms, collapse=" ")))
word_P_B_plot

ggsave(paste("Visualizations/", subject_s, "__Word_P_B_plot_", today("EST"), ".pdf",sep=""), device="pdf")

```
